Interval Probability for Fuzzy Quantum Theories

### 2016-06-04 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} keep updating comments...

%%%%%
\subsection{Quantum Interval-valued Probabilities Measures}
\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
and highly readable until section IV. However, I don't understand
since the second sentence in section IV:
\begin{itemize}
\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
are upper probabilities.
\end{itemize}
I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
Consider the simplest example the subspace $H_{1}$ is the zero space
$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
respectively. The lower probability is $0$ makes sense, but I don't
understand why the upper probability is $1$. Because both the lower
and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
theory.

Start reading \cite{Vourdas2015}...}

>>>>

%%%%%
\subsection{Quantum Interval-valued Probabilities Measures}

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
between the additivity property of Kolmogorov probabilities 
\[
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
\]
and its quantum counterpart 
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
maps a linear space to its projection operator. Since the non-additivity
operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$ is non-zero when
$S_{1}$ and $S_{2}$ does not commute.

However, his section VI is confusing. For example, the second sentence
in section IV: 
\begin{itemize}
\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
are upper probabilities. 
\end{itemize}
I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
Consider the simplest example the subspace $H_{1}$ is the zero space
$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
respectively. The lower probability is $0$ makes sense, but I don't
understand why the upper probability is $1$. Because both the lower
and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
theory.}
